---
title: "R Notebook"
output: html_notebook
---

```{r setup, include = FALSE, message = FALSE}
library(tidyverse)
library(tibble)
library(tibbletime)
library(tidyquant)
library(here)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA)

base_url <- config::get("base_url")
```
 

```{r}
# Build simple model from mtcars dataset
mtcars
# Model ----
cars_model <- lm(mpg ~ cyl + hp,
                 data = mtcars)
tibble(
  hp = 100,
  cyl = 8
) %>% 
predict(cars_model, .)

# Save model ----
saveRDS(cars_model, here( "model-test", "cars-model.rds"))
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

